---
title: "analyses"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
author: "Brian W. Rolek"
date: "May 1, 2021"
output:
  html_document:
    df_print: paged
    toc: yes
  github_document:
    toc: yes
---

<style type="text/css">
  body{
  font-size: 16pt;
}
</style>

Supplemental materials for:
B. W. Rolek, D. J. Harrison, D. W. Linden,  C. S. Loftin, 
P. B. Wood. 2021. Associations among breeding 
conifer-associated birds, forestry treatments, 
years-since-harvest, and vegetation characteristics in 
regenerating stands.  

This RMarkdown document provides a workflow to reproduce analyses of abundance response to forestry treatments.  

# 1. Analyses for Abundance and Vegetation

## 1.1. Abundance and Vegetation Models with a Poisson Distribution and Global Covariates
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('02-analysis_vegetation-pois-global.R')
```
```{r, vegetation Poisson global, eval=FALSE}
```

## 1.2. Abundance and Vegetation Models with a ZIP Distribution and Global Covariates
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('03-analysis_vegetation-zip-global.R')
```
```{r, vegetation ZIP global, eval=FALSE}
```

## 1.3. Abundance and Vegetation Models with a Poisson Distribution and Gibbs Variable Selection
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('04-analysis_vegetation-pois-GVS.R')
```
```{r, vegetation poisson GVS, eval=FALSE}
```

## 1.4. Abundance and Vegetation Models with a ZIP Distribution and Gibbs Variable Selection
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('05-analysis_vegetation-zip-GVS.R')
```
```{r, vegetation ZIP GVS, eval=FALSE}
```

# 2. Analyses for Abundance and Forestry Treatments  

## 2.1. Abundance and Forestry Treatment Models with a Poisson Distribution and Global Covariates
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('02-analysis_treatment-pois-global.R')
```
```{r, treatment Poisson global, eval=FALSE}
```

## 2.2. Abundance  and Forestry Treatment Models with a ZIP Distribution and Global Covariates
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('03-analysis_treatment-zip-global.R')
```
```{r, treatment ZIP global, eval=FALSE}
```

## 2.3. Abundance  and Forestry Treatment Models with a Poisson Distribution and Gibbs Variable Selection
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('04-analysis_treatment-pois-GVS.R')
```
```{r, treatment Poisson GVS, eval=FALSE}
```

## 2.4. Abundance  and Forestry Treatment Models with a ZIP Distribution and Gibbs Variable Selection
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('05-analysis_treatment-zip-GVS.R')
```
```{r, treatment ZIP GVS, eval=FALSE}
```