---
title: "Hierarchical distance removal abundance models"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
author: "Brian W. Rolek"
date: "Oct. 8, 2021"
output:
  html_document:
    df_print: paged
    toc: yes
  github_document:
    toc: yes
---

<style type="text/css">
  body{
  font-size: 16pt;
}
</style>

Unofficial supplemental materials for replicating analyses within:
B. W. Rolek, D. J. Harrison, D. W. Linden,  C. S. Loftin, 
P. B. Wood. 2021. Habitat associations of breeding conifer-associated birds in managed and regenerating forested stands. Forest Ecology and Management 

This RMarkdown document provides R and JAGS code for analyses of abundance in response to vegetation, forestry treatments, and years-since-harvest.  

# 1. Analyses of Abundance using Distance-Removal Models for Point Counts, Basic Models  

## 1.1. Abundance with a Poisson Distribution  
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('01-analysis_basic-models-pois-ZIP.R')
```
```{r, basic Poisson, eval=FALSE}
```

## 1.2. Abundance with a ZIP Distribution  
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('01-analysis_basic-models-pois-ZIP.R')
```
```{r, basic ZIP, eval=FALSE}
```

## 1.3. Calculate Prior Probabilities for Covariates in Gibbs Variable Selection  
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('covariate-prior-probs-for-GVS.R')
```
```{r, Prior probs veg, eval=TRUE, warning=FALSE, error=FALSE}
```
Next we calculate the prior probabilities for treatments and availability covariates in Gibbs variable selection. The two parts of the model happen to have the same model structure with different covariates so we just calculate these prior probabilites once.  
```{r, Prior probs treat, eval=TRUE}
```

# 2. Abundance and Vegetation

## 2.1. Vegetation Covariates, Poisson Distribution, Global Covariates
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('02-analysis_vegetation-pois-global.R')
```
```{r, vegetation Poisson global, eval=FALSE}
```

## 2.2. Vegetation Covariates, ZIP Distribution, Global Covariates
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('03-analysis_vegetation-zip-global.R')
```
```{r, vegetation ZIP global, eval=FALSE}
```

## 2.3. Vegetation Covariates, Poisson Distribution, Gibbs Variable Selection
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('04-analysis_vegetation-pois-GVS.R')
```
```{r, vegetation poisson GVS, eval=FALSE}
```

## 2.4. Vegetation Covariates with a ZIP Distribution and Gibbs Variable Selection
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('05-analysis_vegetation-zip-GVS.R')
```
```{r, vegetation ZIP GVS, eval=FALSE}
```

# 3. Abundance and Forestry Treatments  

## 3.1. Forestry Treatment Covariates, Poisson Distribution, Global Covariates
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('02-analysis_treatment-pois-global.R')
```
```{r, treatment Poisson global, eval=FALSE}
```

## 3.2. Forestry Treatment Covariates, ZIP Distribution, Global Covariates
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('03-analysis_treatment-zip-global.R')
```
```{r, treatment ZIP global, eval=FALSE}
```

## 3.3. Forestry Treatment Covariates, Poisson Distribution, Gibbs Variable Selection
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('04-analysis_treatment-pois-GVS.R')
```
```{r, treatment Poisson GVS, eval=FALSE}
```

## 3.4. Forestry Treatment Covariates, ZIP Distribution, Gibbs Variable Selection
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('05-analysis_treatment-zip-GVS.R')
```
```{r, treatment ZIP GVS, eval=FALSE}
```

