---
title: "run-analyses-treatment"
author: "Brian W. Rolek"
date: "May 1, 2021"
output:
  html_document:
    df_print: paged
    toc: yes
  github_document:
    toc: yes
---

<style type="text/css">
  body{
  font-size: 16pt;
}
</style>

Supplemental materials for:
B. W. Rolek, D. J. Harrison, D. W. Linden,  C. S. Loftin, 
P. B. Wood. 2021. Associations among breeding 
conifer-associated birds, forestry treatments, 
years-since-harvest, and vegetation characteristics in 
regenerating stands. 

This RMarkdown document provides a workflow to reproduce analyses of abundance response to forestry treatments.   

# 1. Run Abundance Models with a Poisson Distribution and Global Covariates
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('02-analysis_treatment-pois-global.R')
```
```{r, treatment Poisson global, eval=FALSE}
```

# 2. Run Abundance Models with a ZIP Distribution and Global Covariates
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('03-analysis_treatment-zip-global.R')
```
```{r, treatment ZIP global, eval=FALSE}
```

# 3. Run Abundance Models with a Poisson Distribution and Gibbs Variable Selection
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('04-analysis_treatment-pois-GVS.R')
```
```{r, treatment Poisson GVS, eval=FALSE}
```

# 4. Run Abundance Models with a ZIP Distribution and Gibbs Variable Selection
```{r, include=FALSE, cache=FALSE}
knitr::read_chunk('05-analysis_treatment-zip-GVS.R')
```
```{r, treatment ZIP GVS, eval=FALSE}
```